A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-03 paper/paper.Rnw
Add plot for brands within shapes

>>>>

<<brands-within-shapes>>=
shapes <- lapply(X = classes, function(x){
  out <- df_shoes[df_shoes[,x, drop = T],]
  out$shape <- x
  out
})
names(shapes) <- classes

shapes %>% map_dfr(., function(x) {
  x %>% group_by(brand) %>%
    summarize(n = n()) %>%
    arrange(desc(n)) %>%
    mutate(prop = n / sum(n),
           shape = x$shape[1:length(n)]) %>%
    head(10)
  }) %>%
  ggplot() +
  geom_text(aes(x = as.factor(shape),
                               y = prop, label = brand,
                               color = as.factor(shape)))
@
